Different forms of uncertainty differently affect the evolution of social learning

### 2022-10-12 ms.tex
fixed error in fixation equation

\paragraph{Stopping conditions} The evolutionary process continues until the
population reaches evolutionary fixation with repsect to social learning, where
$\sum_i s_i = 1$ or $\sum_i s_i = 0$.

>>>>

\paragraph{Stopping conditions} The evolutionary process continues until the
population reaches evolutionary fixation with respect to social learning, where
$\sum_i s_i = N$ or $\sum_i s_i = 0$.
